|

### 2023-07-16 paper/04-results.Rmd
removed footnotes (#14)

In contrast, Figure \ref{fig:fig_crosby_curves_unsucess} shows the feature curves for an unsuccessful pass rush attempt by the Raiders defense from the same game.
In this play, Broncos QB Teddy Bridgewater is well-protected by the offensive line and is able to release a long pass[^unsuccess] to a receiver.
We see that the STRAIN generated by Crosby is relatively small over the course of this play, compared to the previous play (as shown in Figure \ref{fig:fig_crosby_curves}) which results in a sack.

[^unsuccess]: Game footage of this play is available at https://www.nfl.com/videos/teddy-bridgewater-courtland-sutton-barely-miss-out-on-chance-at-62-yard-td-bomb

@@

>>>>

In contrast, Figure \ref{fig:fig_crosby_curves_unsucess} shows the feature curves for an unsuccessful pass rush attempt by the Raiders defense from the same game.
In this [play](https://www.nfl.com/videos/teddy-bridgewater-courtland-sutton-barely-miss-out-on-chance-at-62-yard-td-bomb), Broncos QB Teddy Bridgewater is well-protected by the offensive line and is able to release a long pass to a receiver.
We see that the STRAIN generated by Crosby is relatively small over the course of this play, compared to the previous play (as shown in Figure \ref{fig:fig_crosby_curves}) which results in a sack.

<!-- [^unsuccess]: Game footage of this play is available at https://www.nfl.com/videos/teddy-bridgewater-courtland-sutton-barely-miss-out-on-chance-at-62-yard-td-bomb -->

@@

<!-- ```{r} -->
<!-- #| label: fig_features_combined -->
<!-- #| fig.cap: "Changes in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of a successful pass rush play that results in a sack (left) and an unsuccessful pass rush play which results in a long pass attempt (right). The STRAIN for other pass rushers throughout each play is also displayed." -->
<!-- #| fig.width: 6 -->
<!-- #| fig.height: 3.6 -->
<!-- source(here("scripts", "15_fig_features_combined.R")) -->
<!-- fig_features_combined_bw -->
<!-- ``` -->

<!-- Figure \ref{fig:fig_features_combined} -->
